Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations

### 2019-09-14 notes/paper/paper.tex
revised up to section 4.4

    Let $U(r|M)$ be the profile of a given quantity as a function of the comoving distance $r$ to the centre of a halo of mass $M$, and let $U(k|M)$ be its Fourier transform:
    \begin{equation}
      U(k|M)\equiv4\pi \int_0^\infty dr\,r^2\,\frac{\sin(kr)}{kr}U(r|M).
    \end{equation}
    The halo model prediction for the cross-power spectrum $P_{UV}$ then consists of two contributions, from the so-called 1-halo term and 2-halo term:
    \begin{equation}
      P_{UV}(k)=P^{1h}_{UV}(k)+P^{2h}_{UV}(k).
    \end{equation}
    Each of these can be estimated in terms of the Fourier-space profiles as:
    \begin{align}
      &P^{1h}_{UV}(k)=\int dM\,\frac{dn}{dM}\,\langle U(k|M)\,V(k|M)\rangle,\\
      &P^{2h}_{UV}(k)=\langle bU\rangle\,\langle bV\rangle\,P_L(k),\\
      &\langle bU\rangle(k)\equiv\int dM\frac{dn}{dM}\,b_h(M)\,\langle U(k|M)\rangle. \label{eq:hm_bias}
    \end{align}
    Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function (comoving density of haloes per unit halo mass) and $b_h(M)$ is the halo bias.
    %Further details are discussed in Appendix \ref{app:hm}.

@@

      Putting everything together, the moments of the galaxy overdensity Fourier profile are \citep[e.g. see section 2.2 of][]{2013MNRAS.430..725V}:
      \begin{align}
        &\langle u_g(k)\rangle=\bar{n}_g^{-1}\left[\langle N_c\rangle	+\langle N_s\rangle\,u_s(k)\right],\\
        &\langle |u_g(k)|^2\rangle=\bar{n}_g^{-2}\left[\langle N_s\rangle^2u_s^2(k)+2\langle N_s\rangle u_s(k)\right],
      \end{align}
      where the mean number density $\bar{n}_g$ is
      \begin{equation}
        \bar{n}_g\equiv\int dM\,\frac{dn}{dM}\left(\langle N_c\rangle+\langle N_s\rangle\right),
      \end{equation} 
      and we have suppressed the mass dependence of all quantities for simplicity.

@@

\section{Data}\label{sec:data}
  \subsection{The Compton-$y$ map}\label{ssec:data.y}
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{mask_y.pdf}
      \includegraphics[width=0.5\textwidth]{mask_g.pdf}
      \caption{{\sl Top:} sky mask used for the Compton-$y$ map, corresponding to a sky fraction $f_{\rm sky}=0.59$. {\sl Bottom:} mask used for the 2MPZ and \wisc~ galaxy surveys, corresponding to a sky fraction $f_{\rm sky}=0.68$. The product of both masks leaves a usable sky fraction $f_{\rm sky}\simeq0.58$.
      %The top panel shows, in turquoise, the regions masked additionally when removing sky patches around the position of the tSZ sources detected by \planck\ above 6$\sigma$.
      }
      \label{fig:msk}
    \end{figure}
    We make use of the maps of the Compton-$y$ parameter made public by the Planck collaboration \citep{2016A&A...594A..22P}. These maps were generated using different flavours of the Internal Linear Combination method \citep{2004ApJ...612..633E,2008arXiv0811.4277V}. In a simplified description, the ILC technique selects the linear combination of all frequency channels that preserves the spectrum of the source one wishes to map minimising the map-level variance. The refined versions of the ILC method used by \planck\ further optimise the linear weights on different scales and different regions of the map, and project out sources with known spectra that are likely to cause significant contamination. In particular, the Planck collaboration has released two $y$ maps, extracted using the MILCA \citep{2013A&A...558A.118H} and NILC \citep{2011MNRAS.410.2481R} variations of the ILC technique. Both methods deproject CMB contamination through its well-known spectrum, but differ on the methods used to calculate the optimal scale-dependent and spatially-varying linear weights.

@@

  \subsection{2MPZ and \wisc}\label{ssec:data.g1}
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{nzs.pdf}
      \caption{Fiducial redshift distributions of the different galaxy samples used in this analysis. See Table \ref{tab:z_bins} for further details.}
      \label{fig:dndz}
    \end{figure}
    \begin{table}
      \begin{center}
        \begin{tabular}{l|cccc}
          \hline
          Sample & $[z_{{\rm ph},i},z_{{\rm ph},f}]$ & $\bar{z}$ & $\bar{n}_g\,[{\rm deg}^{-2^{\phantom{2}}}]$ & $\ell_{\rm max}$\\[1ex]
          \hline
          2MPZ    & N.A.         & 0.07 &  25.5 &  280 \\
          \wisc-1 & $[0.1,0.15]$ & 0.13 & 106   &  540 \\
          \wisc-2 & $[0.15,0.2]$ & 0.18 & 126   &  745 \\
          \wisc-3 & $[0.2,0.25]$ & 0.23 & 136   &  945 \\
          \wisc-4 & $[0.25,0.3]$ & 0.27 & 118   & 1130 \\
          \wisc-5 & $[0.3,0.35]$ & 0.32 & 41    & 1310 \\
          \hline
        \end{tabular}
        \caption{Galaxy samples used in this analysis, corresponding to the full 2MPZ survey and five tomographic redshift bins of the \wisc~ survey. The second, third and fourth columns list the photometric redshift interval defining the sample, its mean redshift and its number density respectively. The largest multipole used in the analysis of each sample (corresponding to a comoving scale of $k_{\rm max}\sim 1\,{\rm Mpc}^{-1}$) is shown in the last column.}\label{tab:z_bins}
      \end{center}
    \end{table} 
    We make use of two low-redshift photometric redshift catalogues, the 2MASS Photometric Redshift data set \citep[2MPZ,][]{2014ApJS..210....9B} and the WISE $\times$ SuperCOSMOS catalogue \citep[\wisc,][]{2016ApJS..225....5B}. Both samples were created by cross-matching full-sky imaging surveys, and photo-$z$s were subsequently computed for all the included sources. Their broad photometric coverage, together with adequate spectroscopic calibration data allowed for obtaining well-constrained photo-$z$s, with minimal mean bias, relatively low scatter and a small number of outliers.

    2MPZ was constructed by cross-matching the extended-source catalogue from the 2 Micron All-Sky Survey \citep[2MASS,][]{2006AJ....131.1163S,2000AJ....119.2498J} with the photographic plates of SuperCOSMOS \citep{2001MNRAS.326.1295H,2016MNRAS.462.2085P} and the photometry of the Wide-field Infrared Survey Explorer (WISE: \citejap{2010AJ....140.1868W}). After applying an apparent magnitude cut $K_s<13.9$ to achieve uniformity, 2MPZ includes over 940,000 sources observed in 8 bands: SuperCOSMOS's optical $(B,R,I)$, 2MASS's near-infrared $(J,H,K_s)$ and WISE's mid-infrared $(W1,W2)$. Photometric redshifts (photo-$z$s) were extracted using the neural network code ANNz \citep{2004PASP..116..345C} trained on a large spectroscopic sample from overlapping surveys. The resulting photo-$z$'s have a typical error $\sigma_z\simeq0.015$, and the sample has a median redshift $z\simeq0.08$ (see also \citealt{2018MNRAS.476.1050B} for a more detailed analysis of 2MPZ photo-$z$ properties). As demonstrated in Section \ref{sec:results}, due to the low redshift of this sample, the cross-correlation with the $y$ map is dominated by the 1-halo term for 2MPZ, and little is gained by sub-dividing it into narrower redshift bins. Therefore we use 2MPZ as a single tomographic sample.

@@

    Both 2MPZ and WISC suffer from contamination from Galactic and observational systematics in different levels. The most relevant Galactic systematic is star contamination, particularly for \wisc~ \citep{2018arXiv181208182X}. Besides avoiding regions of high dust and star contamination using the sky mask described in \cite{2018MNRAS.481.1133P} (see bottom panel of Fig.\!~\ref{fig:msk}), we correct for the effects of stellar contamination by correcting for a smooth non-linear relation between galaxy and star density (also described in \citejap{2018MNRAS.481.1133P}). After doing so, three potential sources of systematic uncertainty remain: residual stellar contamination, modulation of the galaxy density due to Galactic dust reddening and modulation due to zero-point fluctuations in the photographic plates used by SuperCOSMOS. We address the first two (dust and stars) by deprojecting them at the map level as described in Section \ref{sssec:methods.syst.deproj}. We address the contamination from fluctuations in the SuperCOSMOS plates by modelling it at the power spectrum level, which we describe in Section \ref{sssec:methods.syst.plates}.

@@

    Although the jackknife method is able to provide an estimate of the size of the power spectrum uncertainties in a model independent way, it also has some drawbacks. There are only so many jackknife regions that can be selected with a reasonable size, and therefore the estimated covariance is noisy at some level. \DA{Typically the number of independent realisations used to estimate a sample covariance matrix should be at least one order of magnitude larger than the size of the data vector (up to 50 elements in our case).} Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction. In order to verify and improve our estimate of the covariance matrix, we make use of a second analytical estimator.

@@

    Fig.\!~\ref{fig:covdiag} shows the diagonal of the covariance matrix for one of the tSZ-galaxy power spectra estimated using these two methods. We find that both estimators are in good agreement with each other. We construct our final fiducial covariance matrix as a hybrid of both estimators: in order to ensure that we recover realistic error bar sizes, we use the variance estimated from the jackknives. We then combine this with the correlation matrix estimated with our analytical method. This ensures that our estimator accounts for the coupling between different modes caused by survey geometry and non-Gaussianities while avoiding the the statistical noise in the jackknife estimator. The final covariance is therefore:
    \begin{equation}
      {\rm Cov}_{ij} = {\rm Cov}^{\rm ana}_{ij} \sqrt{\frac{{\rm Cov}^{\rm JK}_{ii}\,{\rm Cov}^{\rm JK}_{jj}}{{\rm Cov}^{\rm ana}_{ii}\,{\rm Cov}^{\rm ana}_{jj}}},
    \end{equation}
    where ${\rm Cov}^{\rm JK}$ and ${\rm Cov}^{\rm ana}$ are the jackknife and analytical covariance matrices respectively. \DA{We have verified that the resulting covariance matrices are well behaved (i.e. they are invertible, and their eigenvalues have a reasonable dynamical range).}

@@

      The contamination from plate fluctuations can therefore be accounted for as an additive contribution to the model describing the galaxy auto-spectrum, proportional to a template $T_\ell\equiv|W_\ell|^2$ with a free amplitude $A\equiv S_{\rm plate}\sigma_{\rm plate}^2$ that is marginalised over. Since $A$ is a linear parameter, this can be done analytically in a pre-processing step by modifying the inverse covariance matrix of the galaxy auto-spectra as follows \citep{1992ApJ...398..169R}:
      \begin{equation}
        {\sf Cov}^{-1}\hspace{6pt}\rightarrow\hspace{6pt} {\sf Cov}^{-1}-\frac{{\sf Cov}^{-1}{\bf T}\cdot{\bf T}^T{\sf Cov}^{-1}}{{\bf T}^T{\sf Cov}^{-1}{\bf T}},
      \end{equation}
      where ${\bf T}$ is a vector containing the template $T_\ell$ for all the scales used in the analysis. Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$.

@@

      In particular, our interpretation of the $y\times \delta_g$ cross-correlation is especially sensitive to the width of the redshift distributions. This is because, while the amplitude to the galaxy auto-correlation is strongly affected by the width of the distribution (wider $p(z)$ reduce the clustering amplitude), the cross-correlation with $y$ is almost insensitive to it. We therefore introduce an additional parameter $w_z$ that stretches the support of the redshift distribution while preserving unit total probability. Concretely, given a fiducial distribution $p_{\rm fid}(z)$ with mean redshift $\bar{z}$, $w_z$ is implemented as
      \begin{equation}
        p(z)\propto p_{\rm fid}\left(\bar{z}+\frac{z-\bar{z}}{w_z}\right),
      \end{equation}
      where the proportionality constant is fixed by making sure that $p(z)$ integrates to unity. We make $w_z$ a free parameter that we marginalise over with a top-hat prior $0.8<w_z<1.2$. This prior is significantly larger than the actual expected uncertainty in the width of the redshift distributions. To be precise, we estimate that the parameters (e.g. Gaussian mean and variance) of the conditional photo-$z$ distribution $p(z|z_{\rm photo})$ used to calculate the true redshift distributions (Eq.\!~\ref{eq:nz_calc}), are known to the level of $1\%$. When propagated into an uncertainty on the width $w_z$ of $p(z)$, this corresponds to an uncertainty of the same order ($\sim0.9\%$). Thus, the margins of the assumed top-hat priors are wide enough to encompass any lack of precision in the number density distribution.

      \DA{Another possible source of systematic uncertainty is the effect of biased photometric redshifts (i.e. where $\langle z|z_{\rm photo}\rangle\neq z_{\rm photo}$). The ANNz method used in \cite{2018MNRAS.481.1133P} should guarantee unbiased photo-$z$s, but this can never be achieved exactly in practice. It would be possible to account for this form of uncertainty by treating $\bar{z}$ as a free parameter, as is usually done in photometric cosmic shear analyses. Our results, however, are more sensitive to the distribution widths, and we find that this simple parametrisation is able to describe our data sufficiently well. We leave a more detailed analysis of the associated photometric redshift systematics for future work.}

>>>>

    Let $U(r|M)$ be the profile of a given quantity as a function of the comoving distance $r$ to the centre of a halo of mass $M$, and let $U(k|M)$ be its Fourier transform:
    \begin{equation}
      U(k|M)\equiv4\pi \int_0^\infty dr\,r^2\,\frac{\sin(kr)}{kr}U(r|M).
    \end{equation}
    The halo model prediction for the cross-power spectrum $P_{UV}$ then consists of two contributions, from the so-called 1-halo term and 2-halo term:
    \begin{equation}
      P_{UV}(k)=P^{1h}_{UV}(k)+P^{2h}_{UV}(k).
    \end{equation}
    Each of these can be estimated in terms of the Fourier-space profiles as:
    \begin{align}
      &P^{1h}_{UV}(k)=\int dM\,\frac{dn}{dM}\,\langle U(k|M)\,V(k|M)\rangle,\\
      &P^{2h}_{UV}(k)=\langle bU\rangle\,\langle bV\rangle\,P_L(k),\\
      &\langle bU\rangle(k)\equiv\int dM\frac{dn}{dM}\,b_h(M)\,\langle U(k|M)\rangle. \label{eq:hm_bias}
    \end{align}
    Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function (comoving density of haloes per unit halo mass) and $b_h(M)$ is the halo bias.

@@

      Putting everything together, the moments of the galaxy overdensity Fourier profile are \citep[e.g. see section 2.2 of][]{2013MNRAS.430..725V}:
      \begin{align}
        &\langle u_g(k)\rangle=\bar{n}_g^{-1}\left[\langle N_c\rangle	+\langle N_s\rangle\,u_s(k)\right],\\
        &\langle |u_g(k)|^2\rangle=\bar{n}_g^{-2}\left[\langle N_s\rangle^2u_s^2(k)+2\langle N_s\rangle u_s(k)\right],
      \end{align}
      where the mean number density $\bar{n}_g$ is
      \begin{equation}
        \bar{n}_g\equiv\int dM\,\frac{dn}{dM}\left(\langle N_c\rangle+\langle N_s\rangle\right),
      \end{equation} 
      and we have suppressed the mass dependence of all quantities for brevity.

@@

\section{Data}\label{sec:data}
  \subsection{The Compton-$y$ map}\label{ssec:data.y}
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{mask_y.pdf}
      \includegraphics[width=0.5\textwidth]{mask_g.pdf}
      \caption{{\sl Top:} sky mask used for the Compton-$y$ map, corresponding to a sky fraction $f_{\rm sky}=0.59$. {\sl Bottom:} mask used for the 2MPZ and \wisc~ galaxy surveys, corresponding to a sky fraction $f_{\rm sky}=0.68$. The product of both masks leaves a usable sky fraction $f_{\rm sky}\simeq0.58$.
      %The top panel shows, in turquoise, the regions masked additionally when removing sky patches around the position of the tSZ sources detected by \planck\ above 6$\sigma$.
      }
      \label{fig:msk}
    \end{figure}
    We make use of of the Compton-$y$ parameter maps made public by the \planck\ collaboration \citep{2016A&A...594A..22P}. These maps were generated using different flavours of the Internal Linear Combination method \citep{2004ApJ...612..633E,2008arXiv0811.4277V}. In a simplified description, the ILC technique selects the linear combination of all frequency channels that preserves the spectrum of the source one wishes to map minimising the map-level variance. The refined versions of the ILC method used by \planck\ further optimise the linear weights on different scales and different regions of the map, and project out sources with known spectra that are likely to cause significant contamination. In particular, \planck\ has released two $y$ maps, extracted using the MILCA \citep{2013A&A...558A.118H} and NILC \citep{2011MNRAS.410.2481R} variations of the ILC technique. Both methods deproject CMB contamination through its well-known spectrum, but differ on the methods used to calculate the optimal scale-dependent and spatially-varying linear weights.

@@

  \subsection{2MPZ and \wisc}\label{ssec:data.g1}
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{nzs.pdf}
      \caption{Fiducial redshift distributions of the different galaxy samples used in this analysis. See Table \ref{tab:z_bins} for further details.}
      \label{fig:dndz}
    \end{figure}
    \begin{table}
      \begin{center}
        \begin{tabular}{l|cccc}
          \hline
          Sample & $[z_{{\rm ph},i},z_{{\rm ph},f}]$ & $\bar{z}$ & $\bar{n}_g\,[{\rm deg}^{-2^{\phantom{2}}}]$ & $\ell_{\rm max}$\\[1ex]
          \hline
          2MPZ    & N.A.         & 0.07 &  25.5 &  280 \\
          \wisc-1 & $[0.1,0.15]$ & 0.13 & 106   &  540 \\
          \wisc-2 & $[0.15,0.2]$ & 0.18 & 126   &  745 \\
          \wisc-3 & $[0.2,0.25]$ & 0.23 & 136   &  945 \\
          \wisc-4 & $[0.25,0.3]$ & 0.27 & 118   & 1130 \\
          \wisc-5 & $[0.3,0.35]$ & 0.32 & 41    & 1310 \\
          \hline
        \end{tabular}
        \caption{Galaxy samples used in this analysis, corresponding to the full 2MPZ survey and five tomographic redshift bins of the \wisc~ survey. The second, third and fourth columns list the photometric redshift interval defining the sample, its mean redshift and its number density respectively. The largest multipole used in the analysis of each sample (corresponding to a comoving scale of $k_{\rm max}\sim 1\,{\rm Mpc}^{-1}$) is shown in the last column.}\label{tab:z_bins}
      \end{center}
    \end{table} 
    We make use of two low-redshift photometric redshift (photo-$z$) catalogues, the 2MASS Photometric Redshift catalogue \citep[2MPZ,][]{2014ApJS..210....9B} and the WISE $\times$ SuperCOSMOS catalogue \citep[\wisc,][]{2016ApJS..225....5B}. Both samples were created by cross-matching full-sky imaging surveys, and photo-$z$s were subsequently computed for all the included sources. Their broad photometric coverage, together with adequate spectroscopic calibration data allowed for well-constrained photo-$z$s, with minimal mean bias, relatively low scatter and a small number of outliers.

    2MPZ was constructed by cross-matching the extended-source catalogue from the 2 Micron All-Sky Survey \citep[2MASS,][]{2006AJ....131.1163S,2000AJ....119.2498J} with the photographic plates of SuperCOSMOS \citep{2001MNRAS.326.1295H,2016MNRAS.462.2085P} and the photometry of the Wide-field Infrared Survey Explorer (WISE: \citejap{2010AJ....140.1868W}). After applying an apparent magnitude cut $K_s<13.9$ to achieve uniformity, 2MPZ includes over 940,000 sources observed in 8 bands: SuperCOSMOS's optical $(B,R,I)$, 2MASS's near-infrared $(J,H,K_s)$ and WISE's mid-infrared $(W1,W2)$. Photometric redshifts (photo-$z$s) were extracted using the neural network code ANNz \citep{2004PASP..116..345C} trained on a large spectroscopic sample from overlapping surveys. The resulting photo-$z$'s have a typical error $\sigma_z\simeq0.015$, and the sample has a median redshift $z\simeq0.08$ (see also \citealt{2018MNRAS.476.1050B} for a more detailed analysis of the 2MPZ photo-$z$ properties). As demonstrated in Section \ref{sec:results}, due to the low redshift of this sample, the cross-correlation with the $y$ map is dominated by the 1-halo term for 2MPZ, and little is gained by sub-dividing it into narrower redshift bins. Therefore we use 2MPZ as a single tomographic sample.

@@

    Both 2MPZ and WISC suffer from different levels of contamination from Galactic and observational systematics. The most relevant Galactic systematic is star contamination, particularly for \wisc~ \citep{2018arXiv181208182X}. Besides avoiding regions of high dust and star contamination using the sky mask described in \cite{2018MNRAS.481.1133P} (see bottom panel of Fig.\!~\ref{fig:msk}), we correct for the effects of stellar contamination by correcting for a smooth non-linear relation between galaxy and star density (also described in \citejap{2018MNRAS.481.1133P}). After doing so, three potential sources of systematic uncertainty remain: residual stellar contamination, modulation of the galaxy density due to Galactic dust reddening and modulation due to zero-point fluctuations in the photographic plates used by SuperCOSMOS. We address the first two (dust and stars) by deprojecting them at the map level as described in Section \ref{sssec:methods.syst.deproj}. We address the contamination from fluctuations in the SuperCOSMOS plates by modelling it at the power spectrum level, which we describe in Section \ref{sssec:methods.syst.plates}.

@@

    Although the jackknife method is able to provide an estimate of the size of the power spectrum uncertainties in a model independent way, it also has some drawbacks. There are only so many jackknife regions that can be selected with a reasonable size, and therefore the estimated covariance is noisy at some level. Typically, the number of independent realisations used to estimate a sample covariance matrix should be at least one order of magnitude larger than the size of the data vector (up to 50 elements in our case). Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction. In order to verify and improve our estimate of the covariance matrix, we make use of a second analytical estimator.

@@

    Fig.\!~\ref{fig:covdiag} shows the diagonal of the covariance matrix for one of the tSZ-galaxy power spectra estimated using these two methods. We find that both estimators are in good agreement with each other. We construct our final fiducial covariance matrix as a hybrid of both estimators: in order to ensure that we recover realistic error bar sizes, we use the variance estimated from the jackknives. We then combine this with the correlation matrix estimated with our analytical method. This ensures that our estimator accounts for the coupling between different modes caused by survey geometry and non-Gaussianities while avoiding the the statistical noise in the jackknife estimator. The final covariance is therefore:
    \begin{equation}
      {\rm Cov}_{ij} = {\rm Cov}^{\rm ana}_{ij} \sqrt{\frac{{\rm Cov}^{\rm JK}_{ii}\,{\rm Cov}^{\rm JK}_{jj}}{{\rm Cov}^{\rm ana}_{ii}\,{\rm Cov}^{\rm ana}_{jj}}},
    \end{equation}
    where ${\rm Cov}^{\rm JK}$ and ${\rm Cov}^{\rm ana}$ are the jackknife and analytical covariance matrices respectively. We have verified that the resulting covariance matrices are well behaved (i.e. they are invertible, and their eigenvalues have a reasonable dynamical range).

@@

      The contamination from plate fluctuations can therefore be accounted for as an additive contribution to the model describing the galaxy auto-spectrum, proportional to a template $T_\ell\equiv|W_\ell|^2$ with a free amplitude $A\equiv S_{\rm plate}\sigma_{\rm plate}^2$ that is marginalised over. Since $A$ is a linear parameter, this can be done analytically in a pre-processing step by modifying the inverse covariance matrix of the galaxy auto-spectra as follows \citep{1992ApJ...398..169R}:
      \begin{equation}
        {\sf Cov}^{-1}\hspace{6pt}\rightarrow\hspace{6pt} {\sf Cov}^{-1}-\frac{{\sf Cov}^{-1}{\bf T}\cdot{\bf T}^T{\sf Cov}^{-1}}{{\bf T}^T{\sf Cov}^{-1}{\bf T}},
      \end{equation}
      where ${\bf T}$ is a vector containing the template $T_\ell$ for all the scales used in the analysis. Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$ assuming no intrinsic clustering.

@@

      In particular, our model of the $y\times \delta_g$ cross-correlation is especially sensitive to the width of the redshift distributions. This is because, while the amplitude to the galaxy auto-correlation is strongly affected by the width of the distribution (wider $p(z)$s reduce the clustering amplitude), the cross-correlation with $y$ is almost insensitive to it. We therefore introduce an additional parameter $w_z$ that stretches the support of the redshift distribution while preserving unit total probability. Concretely, given a fiducial distribution $p_{\rm fid}(z)$ with mean redshift $\bar{z}$, $w_z$ is implemented as
      \begin{equation}
        p(z)\propto p_{\rm fid}\left(\bar{z}+\frac{z-\bar{z}}{w_z}\right),
      \end{equation}
      where the proportionality constant is fixed by making sure that $p(z)$ integrates to unity. We make $w_z$ a free parameter that we marginalise over with a top-hat prior $0.8<w_z<1.2$. This prior is significantly larger than the actual expected uncertainty in the width of the redshift distributions. To be precise, we estimate that the parameters (e.g. Gaussian mean and variance) of the conditional photo-$z$ distribution $p(z|z_{\rm photo})$ used to calculate the true redshift distributions (Eq.\!~\ref{eq:nz_calc}), are known to the level of $1\%$. When propagated into an uncertainty on the width $w_z$ of $p(z)$, this corresponds to an uncertainty of the same order ($\sim0.9\%$). Thus, the margins of the assumed top-hat priors are wide enough to encompass any lack of precision in the number density distribution.

      Another possible source of systematic uncertainty is the effect of biased photometric redshifts (i.e. where $\langle z|z_{\rm photo}\rangle\neq z_{\rm photo}$). The ANNz method used in \cite{2018MNRAS.481.1133P} should guarantee unbiased photo-$z$s, but this can never be achieved exactly in practice. It would be possible to account for this form of uncertainty by treating $\bar{z}$ as a free parameter, as is usually done in photometric cosmic shear analyses. Our results, however, are more sensitive to the distribution widths, and we find that this simple parametrisation is able to describe our data sufficiently well. We leave a more detailed analysis of the associated photometric redshift systematics for future work.
